References for PloS paper

### 2014-02-17 image_analysis_paper/background_reading/article_notes.tex
Added more notes for background reading

\usepackage{biblatex}

@@

\item \fullcite{jordan2013behavioral}

@@

\item \fullcite{schindler2007inferring}

\item \fullcite{bigot2012geometric}

@@

\item \fullcite{sisan2010event}

>>>>

\usepackage[backend=bibtex]{biblatex}

@@

\item \fullcite{jordan2013behavioral}
\begin{itemize}
	\item Look at phenotypic diversity of the swimming of the ciliate {\em Tetrahymena}
	\item Record the swimming trajectories of many samples over their lifetimes
	\item Define similarity metric between trajectories (compare distributions of speeds and angular velocities)
	\item Use multidimensional scaling (MDS) to embed the trajectories in a lower-dimensional space
	\item Find that there are two ``important'' dimensions that describe all trajectories
	\item Can then look at whether these (low-dimensional) phenotypes are preserved through generations
\end{itemize}

@@

\item \fullcite{schindler2007inferring}
\begin{itemize}
	\item Want to order images that span many years
	\item Solve a constraint satisfaction problem (CSP)
	\item Find features in images, and then try to match up the features between the different images
	\item Use structure from motion (SFM) algorithms to construct 3D points and camera angles from 2D images
	\item Given the sets of features in each image, they then try to order the images in a way that is ``most consistent'' with how buildings are constructed in the real world (i.e. buildings are built, persist for some time, and then can be torn down)-- this is what they call the CSP
\end{itemize}
\item \fullcite{bigot2012geometric}

@@

\item \fullcite{sisan2010event}
\begin{itemize}
	\item Looks at time correlations in data to determine temporal ordering
	\item Goal is to determine in what order cellular events happen (i.e. does rxn A lead to rxn B, or does B lead to A)
	\item They look at the time-correlation between events.
	\item Asymmetry in time-correlation tells you in what order events happen (depending on model)
	\item Looking at time correlation over many samples integrates/averages out stocahsticity in system
\end{itemize}
